Fish_Stuff

### 2024-08-30 R/Fish_ord.Rmd

@@

>>>>

### PERMANOVA

```{r}
herb_perm <- adonis2(species.data.use ~ Herbivore.Biomass + Year + Site + Habitat, data = merged_clean_filtered, dist = 'bray', by = 'margin')
herb_perm
```

##### stratified? 
```{r}
library(permute)
merged_clean_filtered$Site <- as.factor(merged_clean_filtered$Site)
merged_clean_filtered$Habitat <- as.factor(merged_clean_filtered$Habitat)

# Set up the permutation design
perm_design <- how(
  blocks = merged_clean_filtered$Year,  # stratify by Year
  plots = Plots(strata = merged_clean_filtered$Site),  # stratify by Site within Year
  within = Within(type = "free"),  # free permutations within each Site
  nperm = 999  # number of permutations
)

# Apply the permutation design in adonis2
herb_perm <- adonis2(
  species.data.use ~ Herbivore.Biomass + Year + Site + Habitat, 
  data = merged_clean_filtered, 
  dist = 'bray', 
  by = 'margin', 
  permutations = perm_design
)

herb_perm
```

@@

#BECAUSE I LIKE WORKING IN MARKDOWN AND PRINTING IN SCRIPTS:

```{r}
herb_beta <- ggplot(merged_div, aes(x = year)) +
  geom_line(aes(y = centroid_dist_habyear_mean, color = "Centroid Distance")) +
  geom_line(aes(y = Herbivore.Biomass /103388.3, color = "Herbivore Biomass")) + # Rescale Herbivore.Biomass
  facet_grid(site ~ habitat) +
  scale_y_continuous(
    name = "Mean Centroid Distance",
    sec.axis = sec_axis(~ . * 103388.3, name = "Herbivore Biomass") # Rescale back for labeling
  ) +
  scale_color_manual(values = c("Centroid Distance" = "darkgreen", "Herbivore Biomass" = "darkblue")) +
  labs(x = "Year", color = "Legend", title = "Trends in Algal Beta Dispersion and Herbivore Biomass" # Add the plot title here
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
```
